Quantum H theorem, variational entropy, and relaxation processes

### 2020-09-11 notasparaarticulo.tex
Bugfix: bad char. Added gitignore

\bibitem{paradox1}
Harvey R. Brown and Wayne Myrvold, {\it Boltzmannâs H-theorem, its limitations, and thebirth of (fully) statistical mechanics}, physics.hist-ph,0809.1304,2008.

>>>>

\bibitem{paradox1}
Harvey R. Brown and Wayne Myrvold, {\it Boltzmann's H-theorem, its limitations, and thebirth of (fully) statistical mechanics}, physics.hist-ph,0809.1304,2008.
